\let\nofiles\relax
\documentclass[margin]{cv}
%\documentclass[margin,line]{res}
\usepackage[colorlinks=false, bookmarks=false]{hyperref}
\usepackage{enumerate}
\usepackage{etaremune}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\pars
      kip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
      
% Header and footer
\usepackage{lastpage}%获得总页数
\usepackage{fancyhdr}

\resumewidth=1.1\resumewidth
\newsectionwidth{0.8\sectionwidth} % decrease the width of left column(section title)

%\renewcommand{\sc}[1]{{\bf\MakeUppercase{#1}}}

\usepackage{txfonts}


\begin{document}

%\thispagestyle{empty}

%\addtolength{\headheight}{\baselineskip}
\lhead{\hspace*{-\sectionwidth} \sc Aoqian Zhang} % make lhead on the most left
\rhead{\sc Curriculum Vitae}
\cfoot{\thepage~/ \pageref*{LastPage}}
%\pagenumbering{arabic} % choose the page number format: arabic/roman/Roman...

%\addtolength{\headwidth}{-\sectionwidth}
%\addtolength{\headruleskip}{\baselineskip}
\renewcommand{\headrule}{%
  \vskip-0.8\baselineskip\hspace*{-\sectionwidth}\vspace*{1.5\baselineskip} \hrulefill%
  } % make headrule the same width as the textwidth
\pagestyle{fancy}

%\setlength{\headsep}{2in} % space between header and body text

\vspace*{1.5\baselineskip}
\name{{{\fontfamily{phv}\selectfont \LARGE Aoqian Zhang}}}

\begin{resume}
\section{\sc Contact\\ Information}
\vspace{.05in}
\begin{tabular}{@{}p{3.8in}p{3.2in}}
Cheriton School of Computer Science & {\it Phone:}  +1 (226)978 3798 \\            
University of Waterloo   & {\it Email:}  aoqian.zhang@uwaterloo.ca \\
Waterloo, Ontario, Canada, N2L 3G1 & {\it Web:}  \url{https://zaqthss.github.io}\\       

\end{tabular}


\section{\sc Research Interests}

Data Cleaning, Data Imputation, Temporal Anomaly Detection etc.

\section{\sc Education}
{\bf Tsinghua University}, School of Software  \hfill August 2013 - July 2018 \\
Ph.D. in Software Engineering \hfill with \textbf{Graduation Award} \\
Thesis: {\it Research on Time Series Data Cleaning} (Supervisor: Prof. Jianmin Wang)
%Thesis: \textit{Wireless Indoor Localization via Crowdsensing} (Supervisor: Prof. Jianmin Wang)

{\bf Tsinghua University}, School of Software \hfill August 2009 - July 2013 \\
B.E. in Computer Software \hfill with \textbf{Graduation Award} \\

%{\em Department of Statistics} 
%\vspace*{-.1in}
%\begin{list1}
%\item[] Ph.D. Candidate, Computer Science, December 2001 (expected
%  graduation date: May 2003)
%\begin{list2}
%\vspace*{.05in}
%\item Dissertation Topic:  ``Nonstationary Covariance Models for
%  Spatial Data and Regression Problems'' 
%%\item Dissertation Topic:  ``Hierarchical Models for Multiple Ratings
%%  in Performance-Based\\ \hspace*{1.23in} Student Assessments.'' 
%\item Advisor:  Mark J. Schervish
%\end{list2}
%\vspace*{.05in}
%\item[] M.S., Statistics,  May 2000
%\end{list1}

\section{\sc Academic Experience}
{\bf Cheriton School of Computer Science, University of Waterloo}, Waterloo, ON, Canada \\
Post Doctoral Fellows ({\it Advisor: Prof. Ihab Francis Ilyas}) \hfill September 2018 - Now

\section{\sc Honors \& \\ Awards}
{\bf Tsinghua Zi Jing Scholar} ({\it for counsellor who do fantastic job in research}) \hfill 2018 \\
First-class Scholarship (Glodon Scholarship), Tsinghua University \hfill 2014,2017 \\
{\bf Tsinghua Lin Feng Counsellor Prize} ({\it highest honor to counsellors of undergraduates}) \hfill 2016 \\
{\bf National Scholarship, Tsinghua University} \hfill 2015 \\
Excellent Communist Party Member of Master in Tsinghua \hfill 2015 \\
{\bf Data transfer group champion, Solve for tomorrow, National Youth Science Innovation Experiment Competition} \hfill 2013

%\section{\sc Selected Publications}
\section{\sc Publications}

%{\large\bf Journal Papers}

% \begin{enumerate}[{[}J1{]}]
\begin{enumerate}[{[}1{]}]
\item {\bf Aoqian Zhang}, {Shaoxu Song}, {Yu Sun}, {Jianmin Wang}, ``Learning Individual Models for Imputation", 35th {IEEE} International Conference on Data Engineering({\bf ICDE}), Macao, China, April 8-11, 2019, pp. 160-171. 

\item {Shaoxu Song}, {Yu Sun}, {\bf Aoqian Zhang}, {Lei Chen, L}, {Jianmin Wang}  ``Enriching Data Imputation under Similarity Rule Constraints''. IEEE Transactions on Knowledge and Data Engineering({\bf TKDE}) (to appear).

\item {\bf Aoqian Zhang}, {Shaoxu Song}, {Jianmin Wang}, {Philip S. Yu}, ``Time Series Data Cleaning: From Anomaly Detection to Anomaly Repairing'', Proceedings of VLDB({\bf PVLDB}), vol. 10, no. 10, pp. 1046-1057, June 2017.

\item {\bf Aoqian Zhang}, Shaoxu Song, Jianmin Wang, ``Sequential Data Cleaning: A Statistical Approach'', ACM SIGMOD Conference ({\bf ACM SIGMOD}), San Francisco, USA, June 26 - July 1, 2016, pp. 909-924.

\item {Shaoxu Song}, {\bf Aoqian Zhang}, {Lei Chen}, {Jianmin Wang}, ``Enriching Data Imputation with Extensive Similarity Neighbors'', Proceedings of VLDB({\bf PVLDB}), vol. 8, no. 11, pp. 1286-1297, July 2015.

% \end{enumerate}

% {\large\bf Conference Papers}

% \begin{enumerate}[{[}C1{]}]

\item Shaoxu Song, {\bf Aoqian Zhang}, Jianmin Wang, Philip S. Yu, ``SCREEN: Stream Data Cleaning under Speed Constraints'', ACM SIGMOD Conference ({\bf ACM SIGMOD}), Melbourne, VIC, Australia, May 31 - June 4, 2015, pp. 827-841.

\end{enumerate}

\section{\sc Patents}
{\bf Issued Chinese Patents}(2 patents in pending)
\begin{enumerate}[{[}P1{]}]
\item Jianmin Wang, Shaoxu Song, {\bf Aoqian Zhang}, Correction method for global positioning system data based on speed constraint, ZL201711405160.4, issued

\end{enumerate}

\section{\sc Projects}
{\bf TsQaulity}. A project develops data quality tools for large scale time series data, including data profiling, anomaly detection and data repairing. It is one of the projects in the {\bf National Engineering Laboratory for Big Data Software(NEL-BDS)}.

\section{\sc Internship}
Research Intern, Data Engineering Group in K2data, Beijing, China (October 2017 - February 2018)

\section{\sc Professional Services}
\textbf{Reviewer} for ACM Journal of Data and Information Quality

\section{\sc Mentorship}
I am fortunate to work with a great group of graduate and undergraduate students during my PhD time at Tsinghua University:

{\bf Undergraduate Mentorship}

\leftmargini=4mm
\begin{itemize}
\item[-] 2016.07-2017.05: {\bf Director of the Student Affairs Office in School of Software, Tsinghua University}
\item[-] 2015.01-2016.07: {\bf Vice Director of the Student Affairs Office in School of Software, Tsinghua University}
\item[-] 2012.08-2015.07: {\bf Counsellor of over 60 undergraduates of class 2012 in School of Software, Tsinghua University (won over 5 Excellent Collective Awards and the Lin Feng Counsellor Award}
\end{itemize}

\end{resume}
\end{document}



